Download data

### 2023-12-07 scripts/download_dependent_variables.Rmd
generating thinned records

```{r import and clean target species}
targets <- read.csv('../data/raw/2024sos_species.csv', na.strings = "") %>% 
  filter(!species %in% c('tridentata', 'millefolium', 'dioica', 'negundo')) %>%  # purshia,
  unite('taxon', genus:infraspecies, na.rm = T, sep = ' ') # artemisia, and larrea !

@@

records <- bind_rows(aim, bien, gbif1, gbif2, idig) %>% 
  mutate(taxon = str_to_sentence(taxon)) %>% 
  arrange(taxon) # recs need be > 90 m from each other

splicies <- split(records, records$taxon)[1:10]

ONEperCELL <- function(x){

  records <- sf::st_transform(x, 5070) |>
    sf::st_buffer( dist = 90)

  intersects <- sf::st_intersects(records)
  intersect_sets <- unique(intersects) # identify intersected points

  records_list <- vector(mode = 'list', length = length(intersect_sets))
  for (i in seq_along(intersect_sets)){
    records_list[[i]] <- records[unlist((intersect_sets[i])),]
  }

  records_list <- bind_rows(
    lapply(records_list, function(x) x[which.max(x$date),])
  )

  return(records_list)

}

out <- lapply(splicies, ONEperCELL)

```{r}
multiplesPERcell <- function(x){

  records <- sf::st_transform(x, 5070) |>
    sf::st_buffer( dist = 90)

  intersects <- sf::st_intersects(records)
  intersect_sets <- unique(intersects) # identify intersected points

  records_list <- vector(mode = 'list', length = length(intersect_sets))
  for (i in seq_along(intersect_sets)){
    records_list[[i]] <- records[unlist((intersect_sets[i])),]
  }

  max <- bind_rows(
    lapply(records_list, function(x) x[which.max(x$date),])
  )

}
```

>>>>

```{r import and clean target species}
targets <- read.csv('../data/raw/2024sos_species.csv', na.strings = "") %>% 
  filter(!species %in% c('tridentata', 'millefolium', 'dioica', 'negundo')) %>%  # purshia,
  unite('taxon', genus:infraspecies, na.rm = T, sep = ' ') %>% # artemisia, and larrea !
  mutate(taxon = str_squish(taxon))

@@

records <- bind_rows(aim, bien, gbif1, gbif2, idig) %>% 
  mutate(taxon = str_to_sentence(taxon), 
         taxon = str_squish(taxon)) %>% 
  filter(taxon %in% unique(targets$taxon)) %>% 
  arrange(taxon) # recs need be > 90 m from each other

rm(aim, bien, gbif1, gbif2, idig)

splicies <- split(records, records$taxon)

thinned <- lapply(splicies, ONEperCELL)
thinned <- bind_rows(thinned)
write.csv(thinned, '../data/raw/occurrence/thinned_occurrences.csv', row.names = F)
repeated_occurrences <- lapply(splicies, multiplesPERcell)
repeated_occurrences <- purrr::discard(repeated_occurrences, ~nrow(.) < 2)
repeated_occurrences <- bind_rows(repeated_occurrences)
write.csv(repeated_occurrences, '../data/raw/occurrence/repeated_occurrences.csv', row.names = F)

rm(ONEperCELL, multiplesPERcell, records, splicies, repeated_occurrences, base_p)
```
